---
title: "README"
author: "Roger J Bos"
date: "11/30/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Installation

library(devtools)
install_github("rogerjbos/svm_recession)
library(svm_recession)

### Data and sources

The sample data will automatically load and be stored in the object `dat`.  Here are the important variables.

`fwdstate` is 1 if the next month is in a recession and -1 otherwise.
The model is `fwdstate ~ payems + sp500 + yld_curve + man_prod`
where each of the four independant variables includes the current value plus the most recent 11 lagged months, for a total of 48 variables.

* Recessions periods are from the [NBER](https://www.nber.org/cycles.html).
* `payems` is total nonfarm employees from [ALFRED](https://alfred.stlouisfed.org/series?seid=PAYEMS).
* `sp500` is the [S&P 500 monthly closing price](https://www.multpl.com/s-p-500-historical-prices/table/by-month).
* `yld_curve` is [GS10](https://fred.stlouisfed.org/series/GS10) - [FEDFUNDS](https://fred.stlouisfed.org/series/FEDFUNDS) from [FRED](https://fred.stlouisfed.org).
* `man_prod` is the Manufacturing Production Index as published by the Institute for Supply Management(https://www.quandl.com/data/ISM-Institute-for-Supply-Management) downloaded from [Quandl](https://www.quandl.com/data/ISM/MAN_PROD-Manufacturing-Production-Index).

### Running the example


```{r}
library(svm_recession)
best_cost <- 1120
lag <- 12
factors <- "vintage|fwdstate|payems|sp500|yld_curve|man_prod"
fmla = formula(fwdstate ~ .)
cols <- grep(factors, names(dat), value = TRUE)
mydat <- dat[, ..cols]
b1 <- bt(mydat = mydat, fmla = fmla, mylag = 12, best_cost = NA, flip = TRUE)
# Model error rate
b1$error
# Investment strategy preformance
b1$stats  
# Model best cost
b1$best_cost
# First few predictions
tail(b1$ans)
```

### Investment Strategy

The backtest measures the accuracy of the SVM predictions versus the actual recession markers as determined by the NBER.

